Changes in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2020-08-07 analysis/paper/paper.Rmd
remove duplicate site from plot

```{r}
#raw material information
kasr_long1 <- 
  kasr %>% 
  gather(site, 
         count, 
         -X) %>% 
  group_by(site) %>% 
  mutate(percentage = count / sum(count, na.rm = TRUE) * 100,
         total = sum(count, na.rm = TRUE)) %>% 
  filter(!is.na(percentage)) %>% 
  mutate(raw_material = ifelse(percentage >= 10, as.character(X), "other")) %>% 
  mutate(raw_material = ifelse(raw_material == "etc.", "other", raw_material)) %>% 
  select(-X)

  # if percentage is <10%, call it 'other'
kasr_long2 <- 
  kasr_long1 %>% 
  group_by(site, raw_material) %>% 
  summarise(percentage = sum(percentage)) %>% 
  ungroup() %>% 
  left_join(kasr_long1 %>% 
              select(site, raw_material, total),
            by = c('site', "raw_material")) %>% 
  distinct(.keep_all = TRUE) %>%

  # join to get ages of the sites
  left_join(mydata_ages, 
            by = c('site' = 'site_name')) %>% 
  mutate(age_ka = jitter(age_ka),
         age_bin  = ntile(age_ka, 5)) %>% 
  arrange(age_ka) %>% 
  filter(!is.na(age_ka)) %>% 
    mutate(axis_label = glue('{site} ({round(age_ka,1)} ka, n = {total})'))

>>>>

```{r}
#raw material information
kasr_long1 <- 
  kasr %>% 
  gather(site, 
         count, 
         -X) %>% 
  group_by(site) %>% 
  mutate(percentage = count / sum(count, na.rm = TRUE) * 100,
         total = sum(count, na.rm = TRUE)) %>% 
  filter(!is.na(percentage)) %>% 
  # if percentage is <10%, call it 'other'
  mutate(raw_material = ifelse(percentage >= 10, as.character(X), "other")) %>% 
  mutate(raw_material = ifelse(raw_material == "etc.", "other", raw_material)) %>% 
  select(-X)

  # if percentage is <10%, call it 'other'
kasr_long2 <- 
  kasr_long1 %>% 
  group_by(site, raw_material) %>% 
  summarise(percentage = sum(percentage)) %>% 
  ungroup() %>% 
  left_join(kasr_long1 %>% 
              select(site, raw_material, total),
            by = c('site', "raw_material")) %>% 
  distinct(.keep_all = TRUE) %>% 
  # join to get ages of the sites
  left_join(mydata_ages, 
            by = c('site' = 'site_name')) %>% 
 # mutate(age_ka = jitter(age_ka),
 #        age_bin  = ntile(age_ka, 5)) %>% 
  arrange(age_ka) %>% 
  filter(!is.na(age_ka)) %>% 
    mutate(axis_label = glue('{site} ({round(age_ka,1)} ka, n = {total})'))
